Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization

### 2019-05-13 presentation/paperv2.tex
v2

\noindent 
For \textbf{Logistic Lasso} we are interested in examining the impact of the regularization parameter on
the fraction of  non-zero coefficients remaining after regularization is applied and on the impact of the predictive
score on test data. \\

\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
 \hline
 \multicolumn{6}{|c|}{Comparision of Logistic Lasso with different regularization} \\
 \hline
 \multicolumn{1}{|c|}{} &
 \multicolumn{1}{|c|}{} &
 \multicolumn{2}{|c|}{Unstacked} &
 \multicolumn{2}{|c|}{Stacked}\\
 \hline
 N-gram & $\alpha$ & F1 & frac remain & F1 & frac remain\\
 \hline

>>>>

\subsubsection{The impact of regularization coefficient $\alpha$ on logistic regression}
\noindent 
For \textbf{Logistic Lasso} we are interested in examining the impact of the regularization parameter $\alpha$ on
the fraction of  non-zero coefficients remaining after regularization is applied and on the impact of the predictive
score on test data. The results show the regularization parameter at the extremes produces the worst results
and the stacked model has a higher fraction of coefficients eliminated from logistic lasso. The expected result
is the larger regularization parameter reduces the fraction of non-zero coefficients.\\

\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
 \hline
 \multicolumn{6}{|c|}{Comparision of Logistic Lasso varying regularization coefficient $\alpha$} \\
 \hline
 \multicolumn{1}{|c|}{} &
 \multicolumn{1}{|c|}{} &
 \multicolumn{2}{|c|}{Unstacked} &
 \multicolumn{2}{|c|}{Stacked}\\
 \hline
 N-gram & $\alpha$ & F1 & frac remain & F1 & frac remain\\
 \hline
